Revisiting Multi-Domain Machine Translation

### 2020-08-19 2020/tacl2020/rebuttal.tex

\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{definition}{Definition}[section]
\DeclareMathOperator*{\argmax}{argmax}
\newcommand{\R}{\ensuremath{\mathbb{R}}}

\pgfkeys{
    /tr/rowfilter/.style 2 args={
        /pgfplots/x filter/.append code={
            \edef\arga{\thisrow{#1}}
            \edef\argb{#2}
            \ifx\arga\argb
            \else
                \def\pgfmathresult{}
            \fi
        }
    }
}

\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\NewDocumentCommand{\normL}{ s O{} m }{%
  \IfBooleanTF{#1}{\norm*{#3}}{\norm[#2]{#3}}_{L_1}%
}

\title{Responses to the reviews of TACL paper \#2327:
  ``Revisiting Multi-Domain Machine Translation''
}
\author{Action Editor: G. Foster}
\date{}

\begin{document}
\maketitle

\section*{Cover mail}
As TACL action editor for submission 2327, "Revisiting Multi-Domain Machine Translation", I am happy to tell you that I am accepting your paper subject (conditional) to your making specific revisions within two months.

@@

Please address all comments by the reviewers, paying special attention to the following:
\begin{itemize}
	\item Address the concern by reviewer A about the difference between MDL Res and FT-Block, and include FT-block (and ideally FT-Full also) in the later experiments (5.2.2 and 5.3).
	\item Carefully specify the number of parameters for all models, including the proportions that are domain-specific and domain-independent.
	\item Provide all the experimental details requested, and in particular give enough information to allow the corpora to be reproduced, or (ideally) make them publicly available.
\end{itemize}

You are allowed one to two extra pages of content to accommodate these
revisions. To submit your revised version, follow the instructions in the
"Revision and Resubmission Policy for TACL Submissions" section of the
Author Guidelines at
\url{https://transacl.org/ojs/index.php/tacl/about/submissions\#authorGuidelines}.

Thank you for submitting to TACL, and I look forward to your revised
version! \\[2\parskip]

\noindent George Foster\\
\noindent Google Research\\
\noindent geord.foster@gmail.com

@@

770-771), this deterioration is actually small or non-existent when
comparing table 3 and table 5 averages (-0.2 BLEU for DC-Tag; -0.3 BLEU for TTM; +0.9 BLEU for ADM).
\\
\noindent Question to authors:
\item can you describe in more detail the differences between FT-Block and MDL Res, apart from the fact that the former is fine-tuned from a generic model, the latter trained from scratch~?
\textcolor{red}{The two methods use the same architecture composed of one standard Transformer model extended with domain adapters following the design of \cite{Bapna19simple}. As the reviewer correctly points out, the only difference between FT-block and MDL Res is their training process and training data distribution.  

@@

\end{itemize}
\textcolor{red}{The two methods use the same architecture composed of one standard Transformer model extended with domain adapters following the design of \cite{Bapna19simple}. As the reviewer correctly points out, the only difference between FT-block and MDL Res is their training process and training data distribution.  
  \\
  To train FT-block, we plug residual adapters to the output of each self-attention layer of the generic model Mixed-NAT, then resume the training with the learning rate attained at the end of the training the generic model while freezing all of the other parameters of the model Mixed-NAT. For this step, we only use only the in-domain data, as we do during the full-tuning procedure.

@@

  \\
  To train MDL res, we optimize the parameters of the Transformer model and the parameters of the residual adapters from scratch. More precisely, to create a training batch, we randomly pick a domain with a probability equal to the proportion of the domain in training data, and then sample a batch from the corresponding corpora. Given a batch from domain $i$, we simultaneously optimize the parameters of Transformer model and the parameters of the residual adapters for that domain. \\

  We understand that our naming schemes was insisting on procedures, rather than architectures, thus possibly introducing some confusions. We have accordingly changed the name of FT-Block to XXX\fyTodo{fix this}, clarified the description see lines YYY\fyTodo{fix this}, and reported FT-Block as another multidomain system in all tables.\fyTodo{Make sure it is the case}.
}
\noindent Minor issues:
\begin{itemize}
\item I disagree that generalization to unseen domains is similar to zero-shot multilingual MT. In zero-shot multilingual MT, both the source and target distribution have been observed at training time, just paired with other languages. In the generalization to unseen domains, there may be characteristics in the data that were never seen in the training data, including new vocabulary (in the source text, target text, or both).
\item 567-568: "having the domain tag on the source is better than on the target". I assume this refers to the comparison of "DC-Tag" and "TTM". However, TTM actually uses the predicted domain label on the target side, and could perform better with forced decoding of the gold domain label. More precisely, the statement should be that "having the gold tag is better than a predicted tag", but this is hardly surprising.
\end{itemize}

### 2020-08-19 2020/tacl2020/rebuttal.tex

\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{definition}{Definition}[section]
\DeclareMathOperator*{\argmax}{argmax}
\newcommand{\R}{\ensuremath{\mathbb{R}}}

\pgfkeys{
    /tr/rowfilter/.style 2 args={
        /pgfplots/x filter/.append code={
            \edef\arga{\thisrow{#1}}
            \edef\argb{#2}
            \ifx\arga\argb
            \else
                \def\pgfmathresult{}
            \fi
        }
    }
}

\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\NewDocumentCommand{\normL}{ s O{} m }{%
  \IfBooleanTF{#1}{\norm*{#3}}{\norm[#2]{#3}}_{L_1}%
}

\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
\newcommand{\system}[1]{\texttt{\textbf{#1}}}

@@

\title{Responses to the reviews of TACL paper \#2327:
  ``Revisiting Multi-Domain Machine Translation''
}
\author{Action Editor: G. Foster}
\date{}

\begin{document}
\maketitle

The authors wish thank the reviewers and editor for their comments and suggestions, and have tried to address their questions and concerned in the revised version. Details are given below, with pointers to the main changes in the text. Typos and presentations errors have also been corrected in the new submission.

@@

\section*{Cover mail}
As TACL action editor for submission 2327, "Revisiting Multi-Domain Machine Translation", I am happy to tell you that I am accepting your paper subject (conditional) to your making specific revisions within two months.

Please address all comments by the reviewers, paying special attention to the following:
\begin{itemize}
\item Address the concern by reviewer~A about the difference between \system{MDL Res} and \system{FT-Block}, and include \system{FT-block} (and ideally \system{FT-Full} also) in the later experiments (5.2.2 and 5.3). \\
  \textcolor{blue}{discusion XXX.}
\item Carefully specify the number of parameters for all models, including the proportions that are domain-specific and domain-independent. \\
  \textcolor{blue}{New table ...}
\item Provide all the experimental details requested, and in particular give enough information to allow the corpora to be reproduced, or (ideally) make them publicly available.\\
  \textcolor{blue}{Appendix ....}
\end{itemize}

@@

\noindent Question to authors:
\begin{itemize}
\item can you describe in more detail the differences between FT-Block and MDL Res, apart from the fact that the former is fine-tuned from a generic model, the latter trained from scratch~?
  \textcolor{red}{%
    The two methods use the same architecture composed of one standard Transformer model extended with domain adapters following the design of \cite{Bapna19simple}. As the reviewer correctly points out, the only difference between \system{FT-block} and \system{MDL Res} is their training process and training data distribution.
    To train \system{FT-block}, we plug residual adapters to the output of each self-attention layer of the generic model Mixed-NAT, then resume the training with the learning rate attained at the end of the training the generic model while freezing all of the other parameters of the model \system{Mixed-NAT}. For this step, we only use only the in-domain data, as we do during the full-tuning procedure.
    To train MDL res, we optimize the parameters of the Transformer model and the parameters of the residual adapters from scratch. More precisely, to create a training batch, we randomly pick a domain with a probability equal to the proportion of the domain in training data, then sample a batch from the corresponding corpus. Given a batch from domain $i$, we simultaneously optimize the parameters of Transformer model and the parameters of the residual adapters for that domain.
    We understand that our naming schemes was insisting on training procedures, rather than on architectures, thus possibly introducing some confusions. We have accordingly changed the name of \system{FT-Block} to XXX\fyTodo{fix this}, clarified the description of the two systems (see lines YYY\fyTodo{fix this}), and reported \system{FT-Block}\fyTodo{or new name} as another multi-domain system in all tables.\fyTodo{Make sure it is the case}.}
  %}

@@

    We understand that our naming schemes was insisting on training procedures, rather than on architectures, thus possibly introducing some confusions. We have accordingly changed the name of \system{FT-Block} to XXX\fyTodo{fix this}, clarified the description of the two systems (see lines YYY\fyTodo{fix this}), and reported \system{FT-Block}\fyTodo{or new name} as another multi-domain system in all tables.\fyTodo{Make sure it is the case}.}
  %}
\end{itemize}

\noindent\textbf{Minor issues:}
\begin{itemize}
\item I disagree that generalization to unseen domains is similar to zero-shot multilingual MT. In zero-shot multilingual MT, both the source and target distribution have been observed at training time, just paired with other languages. In the generalization to unseen domains, there may be characteristics in the data that were never seen in the training data, including new vocabulary (in the source text, target text, or both).
  \\
  \textcolor{red}{We agree lines XXX}
\item 567-568: "having the domain tag on the source is better than on the target". I assume this refers to the comparison of "DC-Tag" and "TTM". However, TTM actually uses the predicted domain label on the target side, and could perform better with forced decoding of the gold domain label. More precisely, the statement should be that "having the gold tag is better than a predicted tag", but this is hardly surprising.
  \\
  \textcolor{red}{We agree that the conclusion is not really fair for "TTM" because "TTM" intend to predict domain label rather than to use gold domain label and TTM could definitively translate with gold domain label as prefix of each hypothesis.}
    \fyTodo{Check prediction quality, moderate conclusion}
\end{itemize}

@@

\\
I have a few comments:
\\
\item[*] You provide some useful experimental results on various MDMT approaches. To benefit from your results, we need access to the same segmentation of train/dev/test sets that I hope you will provide to the community.
\textcolor{red}{Supplementary details regarding the settings used in our experiments have been added in a new Appendix YYY.\fyTodo{Fix this.}. We will also distribute the detailed composition of our train / dev / test split upon acceptance of the paper.}

@@

\textcolor{red}{Supplementary details regarding the settings used in our experiments have been added in a new Appendix YYY.\fyTodo{Fix this.}. We will also distribute the detailed composition of our train / dev / test split upon acceptance of the paper.}
\\
\item[*] On your discussion on the number of parameters (L. 591), could you share the number of parameters per each MDMT approach~? It will be helpful to see  the impact of the number of parameters on the MT results.
  \textcolor{red}{This information has been added in a new Table~ZZZ \fyTodo{Table number, page and line number and content}.}

@@

\\ 
\item[*] Thinking about your seven operational requirements, I wonder if you could also define a domain or the minimum number of samples to specify a domain. I like your selections of domains that you include multiple domains with varying sizes, but what we expect in extreme cases. Having your Split experiments on REL (Table 4), or providing further details on your last analysis in Section 5.3, if you have tiny clusters could help.

@@

\\
\item[*] Please define Lambda coefficients in lines 142 and 146.

@@

\\
\textcolor{red}{We formalize the data distribution as a mixture of several in-domain distribution. $\lambda$ correspond to the mixing weights, that also define the prior distribution on domains. We hypothesize that training distribution is different from testing distribution, so we have need notation for two different mixtures. This has been clarified in the text (see line~XXX) \fyTodo{add lines}}

@@

\\
\item[*] On dynamically changing the number of training and test domains, there is a new related work published recently that might worth citing it: Sharaf A, Hassan H, Daumé III H. Meta-Learning for Few-Shot NMT Adaptation.

@@

\\
\textcolor{red}{This reference has been added to the related work section.}\fyTodo{Add citation}

@@

\\
\item[*] I’d prefer to see the number of running words in Table~1, especially when the batch size is given as the number of tokens (L. 485).

@@

  \\
  \textcolor{blue}{The table has been updated accordingly.}\fyTodo{to report number of tokens of the datasets}

@@

\\
\item[*] L. 503: It seems you refer to this method as LDR in the rest of the paper. Please make them consistent.
\\
\textcolor{red}{Thanks for pointing this out. We have made this notation more coherent.}

### 2020-08-19 2020/tacl2020/multidomain.tex
revision of the rebutal and of the main text

A typical learning scenario in MT is to have access to samples from $n_d$ domains, which means that the training distribution $\mathcal{D}^s$ is a mixture $\mathcal{D}^s(x) = \sum_d \lambda^{s}_{d} \mathcal{D}_d(x)$. Multi-domain learning, as defined in \cite{Dredze08online} further assumes that domain tags are also available in testing; the implication being that the test distribution is also as a mixture $\mathcal{D}^t(x) = \sum_d \lambda^{t}_{d} \mathcal{D}_d(x)$ of several domains, making the problem distinct from mere domain adaption.  A multi-domain learner is then expected to use these tags effectively \cite{Joshi12multidomain} when computing the combined translation function $h(x,d)$, and to perform well in all domains \cite{Finkel09hierarchical}. Note that this setting is closely related to the multi-source adaptation problem formalized in \cite{Mansour09domainadaptation,Mansour09multiple,Hoffman18algorithms}.

@@

% \cite[eq. (3)]{Wang20general} defines the loss of MDMT as the (macro) average of domain loss - all domains are equally important.
\section{Challenging multi-domain systems \label{sec:challenging}}
In this section, we propose seven\fyDone{check number} operational requirements that can be expected from an effective multi-domain system, and discuss ways to evaluate whether these requirements are actually met. All these evaluations will rest on comparison of translation performance, and do not depend on the choice of a particular metric. To make our results comparable with the literature, we will only use the BLEU score \cite{Papineni02bleu} in Section~\ref{sec:experiments}, noting it may not be the best yardstick to assess subtle improvements of lexical choices that are often associated with domain adapted systems \cite{Irvine13measuring}. Other important figure of merits for MDMT systems are the computational training cost and the total number of parameters.\fyDone{Insert discussion about scores}

\subsection{Multi-domain systems should be effective \label{ssec:effective}}
% \subsubsection{Performance}
A first expectation is that MDMT systems should perform well in the face of mixed-domain test data. This yields the following three requirements.

@@

\subsection{Robustness to fuzzy domain separation \label{ssec:robusness}}
A second set of requirements is related to the definition of a domain. As repeatedly pointed out in the literature, parallel corpora in MT are often collected opportunistically and the view that each corpus constitutes a single domain is often a gross approximation.\footnote{Two of our own ``domains'' actually comprise several subcorpora (IT and MED), see details in section~\ref{ssec:corpora}.} MDMT should aim to make the best of the available data and be robust to domain assignments. To challenge these requirements we propose evaluating the following requirements.

@@

We experiment with translation from English into French and use texts initially originating from 6~domains, corresponding to the following data sources: the UFAL Medical corpus V1.0 (\domain{med})\footnote{\url{https://ufal.mff.cuni.cz/ufal_medical_corpus}}, the European Central Bank corpus (\domain{bank}) \cite{Tiedemann12parallel}; The JRC-Acquis Communautaire corpus (\domain{law}) \cite{Steinberger06acquis}, documentations for KDE, Ubuntu, GNOME and PHP from Opus collection \cite{Tiedemann09news}, collectively merged in a \domain{it}-domain, Ted Talks (\domain{talk}) \cite{Cettolo12wit}, and the Koran (\domain{rel}). Complementary experiments also use v12 of the News Commentary corpus (\domain{news}). Corpus statistics in Table~\ref{tab:Corpora}.  Most corpora are variable from the Opus web site.\footnote{\url{http://opus.nlpl.eu}} These corpora were deduplicated and tokenized with in-house tools. To reduce the number of types and build open-vocabulary systems, we use Byte-Pair Encoding \cite{Sennrich16BPE} with 30,000 merge operations on a corpus containing all sentences in both languages.%

@@

\begin{table*}[htbp]
  \centering
  \begin{tabular}{ |lllllll|} %*{4}{|r|}}
    \hline
    %\multicolumn{4}{|l|}{Vocab size - En: 30,165, Fr: 30,398}\\
    \domain{med} & \domain{law} & \domain{bank} & \domain{it} & \domain{talk} & \domain{rel} & \domain{news} \\
    \hline
    2609 (0.68) & 190 (0.05)  & 501 (0.13) & 270 (0.07) & 160 (0.04) & 130 (0.03) & 260 (0) \\
    \hline
  \end{tabular}
\caption{Corpora statistics: number of parallel lines ($\times 10^3$) and proportion in the basic domain mixture (which does not include the \domain{news} domain). \domain{med} is the largest domain, containing almost 70\% of the sentences, while \domain{rel} is the smallest, with only 3\% of the data.}
\label{tab:Corpora}
\end{table*}

@@

\begin{itemize}
\item a generic model trained on a concatenation of all corpora (\texttt{Mixed}). We develop two versions\footnote{In fact three: to enable a fair comparison with WDCMT, a RNN-based variant is also trained and evaluated.} of this system, one where domain unbalance reflects the distribution of our parallel data (\system{Mixed-Nat}) and one where all domains are equally represented in training (\system{Mixed-Bal}). The former is the best option when the train mixture $\mathcal{D}^s$ is also observed in testing; the latter should be used when the test distribution is uniform across domains. Accordingly, we report two aggregate scores: a weighted average reflecting the default distribution, and an unweighted average, meaning that test domains are equally important.
%   As explained above, depending whether MDMT are expected to perform specially well on large domains, or to treat all domains equally, one or the other training distribution should be prefered.\jcDone{All systems cand be learned following both Bal and Nat. does Nat corresponds to wAVG in test? is wAVG defined somewhere?}
\item fine-tuned models \cite{Luong15stanford,Freitag16fast}\jcDone{i would use Luong and Manning 2015}, based on the \system{Mixed-Nat} system, further trained on each domain for at most 20~000 iterations, with early stopping when the dev BLEU stops increasing. We again contrast two versions: full fine-tuning (\system{FT-Full}), which may update all the parameters of the initial generic model; and the variant of \cite{Bapna19simple}, where fine-tuning only updates a simple adaptation module that is added (with residual connexions) on top of every Transformer layer (\system{FT-Block}).
\end{itemize}

For all models, we set the embeddings size and the hidden layers size to~512. Transformers use multi-head attention with 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 cells. The multi-domain residual system (see description below) additionally uses an adaptation block in each transformer layer, composed of 2-layer perceptron, with an inner RELU activation function operating on normalized entries of dimension 1024. 
% The gated variant is made of a dense layer, followed by a layer normalization and a sigmoid activation.
% The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.
Training use a batch size of~12288 tokens; optimization uses Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$ and Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ for all layers.\fyDone{Describe the block adaptation layer - voir slides} 
 % All our systems are implemented in OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein17opennmt}.
\subsection{Multi-domain systems \label{ssec:systems}}
\fyDone{Remove Gated residual}
Our comparison of multi-domain systems includes the following reimplementations of recent proposals from the literature:
\begin{itemize}
\item a system using domain control as in \cite{Kobus17domaincontrol}: domain information is introduced either as an additional token for each source sentence (\system{DC-Tag}), or introduced in the form of a supplementary feature for each word (\system{DC-Feat}).
\item a system using lexicalized domain representations \cite{Pham19generic}: word embeddings are composed of a generic and a domain specific part (\system{LDR});\fyDone{why not LDR as in Minh's paper?}
\item the three proposals of \newcite{Britz17mixing}. \system{TTM} is a feature-based approach where the domain tag is introduced as an extra word \textsl{on the target side}. Training uses reference tags and inference is performed with predicted tags, just like for regular target words. \system{DM} is a multi-task learner where a domain classifier is trained on top the MT encoder, so as to make it aware of domain differences; \system{ADM} is the adversarial version of \system{DM}, pushing the encoder towards learning domain-independent source representations. These methods thus only use domain tags in training.
\item the multi-domain model of \newcite{Zeng18multidomain} (\system{WDCMT}), where a domain-agnostic and a domain-specialized representation of the input are simultaneously processed; supervised classification and adversarial training are used to compute these representations.\footnote{For this system, we use the available RNN-based system from the authors (\url{https://github.com/DeepLearnXMU/WDCNMT}\fyDone{URLs}) which does not directly compare to the other, Transformer-based, systems; the improved version of \cite{Su19exploring} seems to produce comparable, albeit slightly improved, results.}\fyDone{Check this}
\item an original, multi-domain, version of the approach of \newcite{Bapna19simple}, denoted \system{MDL Res}, where a domain-specific adaptation module is included in all the Transformer layers; within each layer, residual connexions make it possible to by-pass this module.
  % In a variant (\system{MDL Gated}), we use a gating mechanism to merge computations using the the adapter modules and with those that don not.
Contrarily to \cite{Bapna19simple}, we do not start with a trained generic system, but learn the multi-domain from scratch.\fyDone{Check this.}
\end{itemize}

@@

@@

\appendix{}

>>>>

A typical learning scenario in MT is to have access to samples from $n_d$ domains, which means that the training distribution $\mathcal{D}^s$ is a mixture $\mathcal{D}^s(x) = \sum_d \lambda^{s}_{d} \mathcal{D}_d(x)$\textcolor{red}{, with $\{\lambda^{s}_d, d=1 \dots n_d\}$ the corresponding mixture weights ($\sum_d \lambda^{s}_d=1$)}. Multi-domain learning, as defined in \cite{Dredze08online} further assumes that domain tags are also available in testing; the implication being that the test distribution is also as a mixture $\mathcal{D}^t(x) = \sum_d \lambda^{t}_{d} \mathcal{D}_d(x)$ of several domains, making the problem distinct from mere domain adaption.  A multi-domain learner is then expected to use these tags effectively \cite{Joshi12multidomain} when computing the combined translation function $h(x,d)$, and to perform well in all domains \cite{Finkel09hierarchical}. Note that this setting is closely related to the multi-source adaptation problem formalized in \cite{Mansour09domainadaptation,Mansour09multiple,Hoffman18algorithms}.

@@

% \cite[eq. (3)]{Wang20general} defines the loss of MDMT as the (macro) average of domain loss - all domains are equally important.
\section{Challenging multi-domain systems \label{sec:challenging}}
In this section, we propose seven\fyDone{check number} operational requirements that can be expected from an effective multi-domain system, and discuss ways to evaluate whether these requirements are actually met. All these evaluations will rest on comparison of translation performance, and do not depend on the choice of a particular metric. To make our results comparable with the literature, we will only use the BLEU score \cite{Papineni02bleu} in Section~\ref{sec:experiments}, noting it may not be the best yardstick to assess subtle improvements of lexical choices that are often associated with domain adapted systems \cite{Irvine13measuring}. Other important figures of merit for MDMT systems are the computational training cost and the total number of parameters.\fyDone{Insert discussion about scores}

\subsection{Multi-domain systems should be effective \label{ssec:effective}}
% \subsubsection{Performance}
A first expectation is that MDMT systems should perform well in the face of mixed-domain test data. From this, we derive the following three requirements.

@@

\subsection{Robustness to fuzzy domain separation \label{ssec:robusness}}
A second set of requirements is related to the definition of a domain. As repeatedly pointed out in the literature, parallel corpora in MT are often collected opportunistically and the view that each corpus constitutes a single domain is often a gross approximation.\footnote{Two of our own ``domains'' actually comprise several subcorpora (IT and MED), see details in Section~\ref{ssec:corpora}.} MDMT should aim to make the best of the available data and be robust to domain assignments. To challenge these requirements we propose evaluating the following requirements.

@@

We experiment with translation from English into French and use texts initially originating from 6~domains, corresponding to the following data sources: the UFAL Medical corpus V1.0 (\domain{med})\footnote{\url{https://ufal.mff.cuni.cz/ufal_medical_corpus}}, the European Central Bank corpus (\domain{bank}) \cite{Tiedemann12parallel}; The JRC-Acquis Communautaire corpus (\domain{law}) \cite{Steinberger06acquis}, documentations for KDE, Ubuntu, GNOME and PHP from Opus collection \cite{Tiedemann09news}, collectively merged in a \domain{it}-domain, Ted Talks (\domain{talk}) \cite{Cettolo12wit}, and the Koran (\domain{rel}). Complementary experiments also use v12 of the News Commentary corpus (\domain{news}). Corpus statistics in Table~\ref{tab:Corpora}.  Most corpora are variable from the Opus web site.\footnote{\url{http://opus.nlpl.eu}} These corpora were deduplicated and tokenized with in-house tools. To reduce the number of types and build open-vocabulary systems, we use Byte-Pair Encoding \cite{Sennrich16BPE} with 30,000 merge operations on a corpus containing all sentences in both languages.\fyTodo{Add \# number of tokens, also specificity ?}%

@@

\begin{table*}[htbp]
  \centering
  \begin{tabular}{|l|rrrrrrr|} %*{4}{|r|}}
    \cline{2-8} 
    %\multicolumn{4}{|l|}{Vocab size - En: 30,165, Fr: 30,398}\\
    \multicolumn{1}{c|}{} & \multicolumn{1}{c}{\domain{med}} & \multicolumn{1}{c}{\domain{law}} & \multicolumn{1}{c}{\domain{bank}} & \multicolumn{1}{c}{\domain{it}} & \multicolumn{1}{c}{\domain{talk}} & \multicolumn{1}{c}{\domain{rel}} & \multicolumn{1}{c|}{\domain{news}} \\
    \hline 
    \# lines & 2609 (0.68) & 190 (0.05)  & 501 (0.13) & 270 (0.07) & 160 (0.04) & 130 (0.03) & 260 (0) \\
    \# \textcolor{red}{tokens} &  XX  & XX &  XX &  XX &  XX &  XX &  XX  \\
    \hline
  \end{tabular}
\caption{Corpora statistics: number of tokens ($\times 10^6$), number of parallel lines ($\times 10^3$) and proportion in the basic domain mixture (which does not include the \domain{news} domain). \domain{med} is the largest domain, containing almost 70\% of the sentences, while \domain{rel} is the smallest, with only 3\% of the data.}
\label{tab:Corpora}
\end{table*}

@@

\begin{itemize}
\item a generic model trained on a concatenation of all corpora (\texttt{Mixed}). We develop two versions\footnote{In fact three: to enable a fair comparison with WDCMT, a RNN-based variant is also trained and evaluated.} of this system, one where domain unbalance reflects the distribution of our parallel data (\system{Mixed-Nat}) and one where all domains are equally represented in training (\system{Mixed-Bal}). The former is the best option when the train mixture $\mathcal{D}^s$ is also observed in testing; the latter should be used when the test distribution is uniform across domains. Accordingly, we report two aggregate scores: a weighted average reflecting the default distribution, and an unweighted average, meaning that test domains are equally important.
%   As explained above, depending whether MDMT are expected to perform specially well on large domains, or to treat all domains equally, one or the other training distribution should be prefered.\jcDone{All systems cand be learned following both Bal and Nat. does Nat corresponds to wAVG in test? is wAVG defined somewhere?}
\item fine-tuned models \cite{Luong15stanford,Freitag16fast}\jcDone{i would use Luong and Manning 2015}, based on the \system{Mixed-Nat} system, further trained on each domain for at most 20~000 iterations, with early stopping when the dev BLEU stops increasing. We again contrast two versions: full fine-tuning (\system{FT-Full}), which may update all the parameters of the initial generic model; and the variant of \cite{Bapna19simple}, where fine-tuning only updates a simple adaptation module that is added (with residual connections) on top of every Transformer layer (\system{FT-Block}).
\end{itemize}

For all models, we set the embeddings size and the hidden layers size to~512. Transformers use multi-head attention with 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 cells. The multi-domain residual system (see description below) additionally uses an adaptation block in each transformer layer, composed of 2-layer perceptron, with an inner RELU activation function operating on normalized entries of dimension 1024. 
% The gated variant is made of a dense layer, followed by a layer normalization and a sigmoid activation.
% The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.
Training use a batch size of~12288 tokens; optimization uses Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$ and Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ for all layers.\fyDone{Describe the block adaptation layer - voir slides} 
 % All our systems are implemented in OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein17opennmt}.
\subsection{Multi-domain systems \label{ssec:systems}}
\fyDone{Remove Gated residual}
Our comparison of multi-domain systems includes the following reimplementations of recent proposals from the literature:
\begin{itemize}
\item a system using domain control as in \cite{Kobus17domaincontrol}: domain information is introduced either as an additional token for each source sentence (\system{DC-Tag}), or introduced in the form of a supplementary feature for each word (\system{DC-Feat}).
\item a system using lexicalized domain representations \cite{Pham19generic}: word embeddings are composed of a generic and a domain specific part (\system{LDR});\fyDone{why not LDR as in Minh's paper?}
\item the three proposals of \newcite{Britz17mixing}. \system{TTM} is a feature-based approach where the domain tag is introduced as an extra word \textsl{on the target side}. Training uses reference tags and inference is performed with predicted tags, just like for regular target words. \system{DM} is a multi-task learner where a domain classifier is trained on top the MT encoder, so as to make it aware of domain differences; \system{ADM} is the adversarial version of \system{DM}, pushing the encoder towards learning domain-independent source representations. These methods thus only use domain tags in training.
\item the multi-domain model of \newcite{Zeng18multidomain} (\system{WDCMT}), where a domain-agnostic and a domain-specialized representation of the input are simultaneously processed; supervised classification and adversarial training are used to compute these representations.\footnote{For this system, we use the available RNN-based system from the authors (\url{https://github.com/DeepLearnXMU/WDCNMT}\fyDone{URLs}) which does not directly compare to the other, Transformer-based, systems; the improved version of \cite{Su19exploring} seems to produce comparable, albeit slightly improved, results.}\fyDone{Check this}
\item an original, multi-domain, version of the approach of \newcite{Bapna19simple}, denoted \system{MDL Res}, where a domain-specific adaptation module is included in all the Transformer layers; within each layer, residual connections make it possible to by-pass this module.
  % In a variant (\system{MDL Gated}), we use a gating mechanism to merge computations using the the adapter modules and with those that don not.
Contrarily to \cite{Bapna19simple}, we do not start with a trained generic system, but learn the multi-domain from scratch.\fyDone{Check this.}
\end{itemize}

@@

\newpage\newpage
\section*{Appendices}

\subsection*{A - Description of multi-domain systems}

The description of model in each MDMT approach is as follows:
\begin{itemize}
\item \system{Mixed-NAT}, \system{FT-full}, \system{TTM}, \system{DC-Tag} use the medium Transformer model (\fyTodo{ref})
\item \system{FT-block} and \system{MDL res} use medium Transformer model, and residual layers with the bottleneck dimension of size 1024. \cite{Bapna19simple} showed that if the bottleneck dimension is large enough, the gap between \system{FT-block} and \system{FT-full} will be small.\fyTodo{This comment is confusing}.
\item \system{ADM}, \system{DM} use medium Tranformer model and a domain classifier composing of 3 dense layers of size $512 \times 2048$, $2048 \times 2048$ and $2048 \times domain\_num$. The two first layers of the classifier use the $\operatorname{ReLU}()$ as activation function, the last layer uses $\tanh()$ as activation function.
\item \system{DC-Feat} uses medium Transformer model and domain embeddings of size 4. Given a sentence of domain~$i$ in a training batch, the embedding of domain $i$ is concatenated to the embedding of each token in the sentence.
\item \system{LDR} uses medium Transformer model and for each token we introduce a \system{LDR} feature of size $4 \times domain\_num$. Given a sentence of domain $i\in[1,..,K]$ in the training batch, for each token of the sentence, the \system{LDR} units of the indexes outside of the range $[4(i-1),..,4i-1]$ are masked to 0, the masked LDR feature will be concatenated to the embedding of the token. Details are in \cite{Pham19generic}.
\item \system{WDCNMT} uses one layer GRU bidirectional as encoder and one layer GRU-conditional as decoder. The size of each hidden layer is 1024, the size of word embedding is 512.
\item \system{Mixed-NAT-RNN} uses one layer LSTM bidirectional as encoder and one layer LSTM as decoder. The size of each hidden layer is 1024, the size of word embeddings is 512. 
\end{itemize}

@@
